---
title: "Assignment"
author: "Aalii Kelling"
date: "2023-08-23"
output: github_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(ggplot2)
library(dplyr)
library(rmarkdown)
library(devtools)
library(fishualize)
library(raster)
```

```{r}
library(raster)
library(habtools)
library(devtools)
library(ggplot2)
library(dplyr)
library(fishualize)

plot(horseshoe)

```

### Current Lab
Johansen Fish Resilience Lab

### Project Focus
Imu kai as artificial reef systems

### Why you chose this course
I chose to enroll in this course because I am interested in learning more about structure for motion and how I can apply this technique into my own project.

### What do you want to learn about the most in this course
I would like to learn more about how to effectively measure habitat complexity as vertical topography changes.

### Your R experience
I have taken a couple R courses and still navigating my way through this amazing program. I hope that this course will help me feel more comfortable with R and gain several new skills. 

### Fun fact  

My favorite food is crab! 
